Advancing Renewable Gas Storage using Flat-histogram Methods

### 2020-05-27 dissertation/abstract.tex
added a new dissertation tex which conforms to OSU guidlines.

%\thispagestyle{plain}
\thispagestyle{empty}
\begin{center}
	\large
	AN ABSTRACT OF THE DISSERTATION OF
\end{center}

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
\nobreak presented on \underline{June 8, 2020}
\vspace{1.0cm}

\justify{}
Title: \underline{Advancing Renewable Gas Storage using Flat-histogram Methods}.
\vspace{2.0cm}

\justify{}
Abstract approved:
\underline{\hspace{11cm}}
\vspace{0.1cm}

%\centering{}
\hspace{7.0cm} David J. Roundy
\vspace{1.0cm}

\justify{}
\doublespacing
This work introduces the novel flat-histogram Monte
Carlo (MC) method stochastic approximation with a dynamic update factor (SAD) and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a number of physical `test’ systems including the 2D Ising model, a
square-well fluid, and a Lennard-Jones cluster. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all properties of interest for any given MOF thereby providing a powerful way for researchers to determine any porous media's suitability for gas storage applications.

\newpage{}
\thispagestyle{empty}
\singlespacing

\vspace*{4.0cm}
\begin{center}
$\copyright$ Copyright by Jordan K. Pommerenck \\
June 8, 2020 \\
All Rights Reserved
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing

\begin{center}
Advancing Renewable Gas Storage using Flat-histogram Methods

\vspace{1.0cm}
by \\
Jordan K. Pommerenck \\
\vspace{3.0cm}
A DISSERTATION \\
\vspace{0.5cm}
submitted to \\
\vspace{0.5cm}
Oregon State University \\
\vspace{3.0cm}
in partial fulfillment of \\
the requirements for the \\
degree of \\
\vspace{1.0cm}
Doctor of Philosophy \\
\vspace{3.0cm}
Presented June 8, 2020  \\
Commencement June 2020
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing
\justify{}
\underline{Doctor of Philosophy} dissertation of \underline{Jordan K. Pommerenck} presented on
\underline{June 8, 2020.} \\

\justify{}
\vspace{0.5cm}
APPROVED: \\

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Major Professor, representing Physics
\vspace{1.0cm}
\end{flushleft}

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Head of the Department of Physics
\vspace{1.0cm}
\end{flushleft}

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Dean of the Graduate School
\vspace{1.0cm}
\end{flushleft}

\vspace{3.0cm}
\justify{}
I understand that my dissertation will become part of the permanent collection
of Oregon State University libraries. My signature below authorizes release of my dissertation to any reader upon request. \\
\vspace{0.5cm}
\begin{flushleft}
\underline{\hspace{15cm}}
\end{flushleft}
\centering{}
Jordan K. Pommerenck, Author

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off approach to advising have tremendously helped my development as an independent scientific researcher. I express thanks to my entire graduate committee: David McIntyre, Davide Lazzati, Yun-Shik Lee, and graduate council representative Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding undergraduate and graduate students that have positively impacted me personally and professionally while at Oregon State University. Finally, I would like to thank my parents for their unconditional support throughout my Ph.D. research.

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	CONTRIBUTION OF AUTHORS
\end{center}
\justify{}
\doublespacing
Michael A. Perlin worked on much of the early C{}\verb!++! codebase. This codebase was used primarily in the early study of many of the MC methods before switching to RUST. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}. 
Tanner T. Simpson performed many of the early simulations for the flat-histogram methods using the C{}\verb!++! codebase. He also developed using Python some of the plotting scripts that allowed the saved C{}\verb!++! data to be visualized. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}.
Cory M. Simon collaborated together with us on the third manuscript \emph{An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials}. He contributed significantly to the introduction section of the paper and helped in the editing phase throughout preparation. In addition, he designed the first figure in the paper and the first figure in the supplemental to the paper.

>>>>

This work introduces the novel flat-histogram Monte Carlo (MC) method
stochastic approximation with a dynamic update factor (SAD) and explores the
convergence properties of a variety of related weight-based MC methods. The new
method is applied to a number of physical `test’ systems including the 2D Ising
model, a square-well fluid, and a Lennard-Jones cluster. A driving motivation
for developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and delivery in
metal-organic frameworks is developed and compared with experimental data. SAD
is introduced as a powerful method for examining thermodynamic properties for
MOFs. A preliminary groundwork is laid for the future development of a
multi-dimensional SAD which would be able to compute all properties of interest
for any given MOF thereby providing a powerful way for researchers to determine
any porous media's suitability for gas storage applications.

### 2020-05-27 dissertation/acknowledgements.tex
added a new dissertation tex which conforms to OSU guidlines.

%\thispagestyle{plain}
\thispagestyle{empty}
\begin{center}
	\large
	AN ABSTRACT OF THE DISSERTATION OF
\end{center}

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
\nobreak presented on \underline{June 8, 2020}
\vspace{1.0cm}

\justify{}
Title: \underline{Advancing Renewable Gas Storage using Flat-histogram Methods}.
\vspace{2.0cm}

\justify{}
Abstract approved:
\underline{\hspace{11cm}}
\vspace{0.1cm}

%\centering{}
\hspace{7.0cm} David J. Roundy
\vspace{1.0cm}

\justify{}
\doublespacing
This work introduces the novel flat-histogram Monte
Carlo (MC) method stochastic approximation with a dynamic update factor (SAD) and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a number of physical `test’ systems including the 2D Ising model, a
square-well fluid, and a Lennard-Jones cluster. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all properties of interest for any given MOF thereby providing a powerful way for researchers to determine any porous media's suitability for gas storage applications.

\newpage{}
\thispagestyle{empty}
\singlespacing

\vspace*{4.0cm}
\begin{center}
$\copyright$ Copyright by Jordan K. Pommerenck \\
June 8, 2020 \\
All Rights Reserved
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing

\begin{center}
Advancing Renewable Gas Storage using Flat-histogram Methods

\vspace{1.0cm}
by \\
Jordan K. Pommerenck \\
\vspace{3.0cm}
A DISSERTATION \\
\vspace{0.5cm}
submitted to \\
\vspace{0.5cm}
Oregon State University \\
\vspace{3.0cm}
in partial fulfillment of \\
the requirements for the \\
degree of \\
\vspace{1.0cm}
Doctor of Philosophy \\
\vspace{3.0cm}
Presented June 8, 2020  \\
Commencement June 2020
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing
\justify{}
\underline{Doctor of Philosophy} dissertation of \underline{Jordan K. Pommerenck} presented on
\underline{June 8, 2020.} \\

\justify{}
\vspace{0.5cm}
APPROVED: \\

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Major Professor, representing Physics
\vspace{1.0cm}
\end{flushleft}

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Head of the Department of Physics
\vspace{1.0cm}
\end{flushleft}

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Dean of the Graduate School
\vspace{1.0cm}
\end{flushleft}

\vspace{3.0cm}
\justify{}
I understand that my dissertation will become part of the permanent collection
of Oregon State University libraries. My signature below authorizes release of my dissertation to any reader upon request. \\
\vspace{0.5cm}
\begin{flushleft}
\underline{\hspace{15cm}}
\end{flushleft}
\centering{}
Jordan K. Pommerenck, Author

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off approach to advising have tremendously helped my development as an independent scientific researcher. I express thanks to my entire graduate committee: David McIntyre, Davide Lazzati, Yun-Shik Lee, and graduate council representative Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding undergraduate and graduate students that have positively impacted me personally and professionally while at Oregon State University. Finally, I would like to thank my parents for their unconditional support throughout my Ph.D. research.

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	CONTRIBUTION OF AUTHORS
\end{center}
\justify{}
\doublespacing
Michael A. Perlin worked on much of the early C{}\verb!++! codebase. This codebase was used primarily in the early study of many of the MC methods before switching to RUST. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}. 
Tanner T. Simpson performed many of the early simulations for the flat-histogram methods using the C{}\verb!++! codebase. He also developed using Python some of the plotting scripts that allowed the saved C{}\verb!++! data to be visualized. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}.
Cory M. Simon collaborated together with us on the third manuscript \emph{An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials}. He contributed significantly to the introduction section of the paper and helped in the editing phase throughout preparation. In addition, he designed the first figure in the paper and the first figure in the supplemental to the paper.

>>>>

I gratefully acknowledge my graduate advisor David Roundy for his constant
support and guidance throughout my research. His breadth of knowledge and
hands-off approach to advising have tremendously helped my development as an
independent scientific researcher. I express thanks to my entire graduate
committee: David McIntyre, Davide Lazzati, Yun-Shik Lee, and graduate council
representative Chih-hung (Alex) Chang. I would like to acknowledge the many
outstanding undergraduate and graduate students that have positively impacted
me personally and professionally while at Oregon State University. Finally, I
would like to thank my parents for their unconditional support throughout my
Ph.D. research.

### 2020-05-27 dissertation/contributors.tex
added a new dissertation tex which conforms to OSU guidlines.

%\thispagestyle{plain}
\thispagestyle{empty}
\begin{center}
	\large
	AN ABSTRACT OF THE DISSERTATION OF
\end{center}

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
\nobreak presented on \underline{June 8, 2020}
\vspace{1.0cm}

\justify{}
Title: \underline{Advancing Renewable Gas Storage using Flat-histogram Methods}.
\vspace{2.0cm}

\justify{}
Abstract approved:
\underline{\hspace{11cm}}
\vspace{0.1cm}

%\centering{}
\hspace{7.0cm} David J. Roundy
\vspace{1.0cm}

\justify{}
\doublespacing
This work introduces the novel flat-histogram Monte
Carlo (MC) method stochastic approximation with a dynamic update factor (SAD) and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a number of physical `test’ systems including the 2D Ising model, a
square-well fluid, and a Lennard-Jones cluster. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all properties of interest for any given MOF thereby providing a powerful way for researchers to determine any porous media's suitability for gas storage applications.

\newpage{}
\thispagestyle{empty}
\singlespacing

\vspace*{4.0cm}
\begin{center}
$\copyright$ Copyright by Jordan K. Pommerenck \\
June 8, 2020 \\
All Rights Reserved
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing

\begin{center}
Advancing Renewable Gas Storage using Flat-histogram Methods

\vspace{1.0cm}
by \\
Jordan K. Pommerenck \\
\vspace{3.0cm}
A DISSERTATION \\
\vspace{0.5cm}
submitted to \\
\vspace{0.5cm}
Oregon State University \\
\vspace{3.0cm}
in partial fulfillment of \\
the requirements for the \\
degree of \\
\vspace{1.0cm}
Doctor of Philosophy \\
\vspace{3.0cm}
Presented June 8, 2020  \\
Commencement June 2020
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing
\justify{}
\underline{Doctor of Philosophy} dissertation of \underline{Jordan K. Pommerenck} presented on
\underline{June 8, 2020.} \\

\justify{}
\vspace{0.5cm}
APPROVED: \\

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Major Professor, representing Physics
\vspace{1.0cm}
\end{flushleft}

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Head of the Department of Physics
\vspace{1.0cm}
\end{flushleft}

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Dean of the Graduate School
\vspace{1.0cm}
\end{flushleft}

\vspace{3.0cm}
\justify{}
I understand that my dissertation will become part of the permanent collection
of Oregon State University libraries. My signature below authorizes release of my dissertation to any reader upon request. \\
\vspace{0.5cm}
\begin{flushleft}
\underline{\hspace{15cm}}
\end{flushleft}
\centering{}
Jordan K. Pommerenck, Author

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off approach to advising have tremendously helped my development as an independent scientific researcher. I express thanks to my entire graduate committee: David McIntyre, Davide Lazzati, Yun-Shik Lee, and graduate council representative Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding undergraduate and graduate students that have positively impacted me personally and professionally while at Oregon State University. Finally, I would like to thank my parents for their unconditional support throughout my Ph.D. research.

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	CONTRIBUTION OF AUTHORS
\end{center}
\justify{}
\doublespacing
Michael A. Perlin worked on much of the early C{}\verb!++! codebase. This codebase was used primarily in the early study of many of the MC methods before switching to RUST. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}. 
Tanner T. Simpson performed many of the early simulations for the flat-histogram methods using the C{}\verb!++! codebase. He also developed using Python some of the plotting scripts that allowed the saved C{}\verb!++! data to be visualized. In addition, he helped in the editing phase during the preparation of the first manuscript \emph{Stochastic approximation Monte Carlo with a dynamic update factor}.
Cory M. Simon collaborated together with us on the third manuscript \emph{An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials}. He contributed significantly to the introduction section of the paper and helped in the editing phase throughout preparation. In addition, he designed the first figure in the paper and the first figure in the supplemental to the paper.

>>>>

Michael A. Perlin worked on much of the early C{}\verb!++! codebase. This
codebase was used primarily in the early study of many of the MC methods before
switching to RUST. In addition, he helped in the editing phase during the
preparation of the first manuscript \emph{Stochastic approximation Monte Carlo
with a dynamic update factor}. Tanner T. Simpson performed many of the early
simulations for the flat-histogram methods using the C{}\verb!++! codebase. He
also developed using Python some of the plotting scripts that allowed the saved
C{}\verb!++! data to be visualized. In addition, he helped in the editing phase
during the preparation of the first manuscript \emph{Stochastic approximation
Monte Carlo with a dynamic update factor}. Cory M. Simon collaborated together
with us on the third manuscript \emph{An upper bound to gas delivery via
pressure-swing adsorption in nanoporous materials}. He contributed
significantly to the introduction section of the paper and helped in the
editing phase throughout preparation. In addition, he designed the first figure
in the paper and the first figure in the supplemental to the paper.

### 2020-05-27 dissertation/dissertation.tex
added a new dissertation tex which conforms to OSU guidlines.

\documentclass[double,12pt]{beavtex}
\usepackage{graphicx}
\usepackage{rotating} %Package added to allow the rotation of figures and chart on a page, {sidewaysfigure} command
\usepackage{tablefootnote} %Packaged added to allow footnotes in the tabular environment, use \tablefootnote command

@@

\title{Branching Random Walk and Probability Problems
from Physics and Biology}
\author{Torrey Johnson}
\degree{Doctor of Philosophy}
\doctype{Dissertation}
\department{Mathematics}
\depttype{Department}
\depthead{Chair}
\major{Mathematics}
\advisor{Edward C Waymire}
\submitdate{June 7, 2012}
\commencementyear{2013}
\abstract{\input{chapter-5.tex}}
\acknowledgements{\input{chapter-5.tex}}

@@

\begingroup
\let\clearpage\relax
\begin{center}
\large
Branching Random Walk and Probability Problems
from Physics and Biology
\normalsize
\end{center}
\chapter{Introduction}
hello this is the chapter
%\input{introduction.tex}
\endgroup

% \chapter{Tree Polymers in the Infinite Volume Limit at Critical Strong Disorder}
% \input{csd.tex}

% \chapter{Simple Branching Random Walk and an Associated Tree Polymer}
% \input{brwtree.tex}

% \chapter{Branching for a Decision: A Site-Selection Model for Honeybee Swarms}
% \input{beetext.tex}

% \chapter{Conclusion}
% \input{conclusion.tex}

% \bibliographystyle{plain}
% \bibliography{bib}

% \appendix
% \chapter{Code for Swarm Simulation}
% \input{appendix.tex}
\end{document}

>>>>

\documentclass[double,12pt]{beavtex}

\usepackage{fancyhdr}
% link to section command
\newcommand{\HR}[1]{\textbf{\hyperref[#1]{\ref{#1}}}}

% for creating an index at end of document
\usepackage{imakeidx}
\makeindex[columns=1, title=Alphabetical Index]

% indexing commands
\newcommand{\bind}[1]{\textbf{#1}\index{#1}}
\newcommand{\iind}[1]{\textit{#1}\index{#1}}
\newcommand{\ind}[1]{#1\index{#1}}

\usepackage[hypertexnames=false]{hyperref}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Pommerenck Thesis},    % title
    pdfauthor={Jordan K. Pommerenck},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={flat-histogram, Monte Carlo, Thesis}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links (change box color with linkbordercolor)
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
%\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
% differential and partials package
\usepackage[thinc]{esdiff}
\usepackage{physics}
\newcommand{\D}[1]{\text{d}#1}
% the nth superscript package
\usepackage[super]{nth}

\usepackage{indentfirst}
\usepackage{graphicx}
\graphicspath{{../square-well/}{../ising/}{../gas-adsorption/figs/}}

\usepackage{caption}
%\usepackage{subcaption}
\usepackage{float}
\usepackage{amsmath,amssymb}
\usepackage{nicefrac}

% Use more than one optional parameter in a new commands
\usepackage{xargs}
\usepackage[pdftex,dvipsnames]{xcolor}
\usepackage[colorinlistoftodos,prependcaption,textsize=normalsize]{todonotes}
\usepackage{mdframed}
\usepackage{braket}

% gas adsorption commands
\usepackage{subfig}
\usepackage{url}
%
\usepackage[colorinlistoftodos,prependcaption,textsize=normalsize]{todonotes}

\newcommand{\addcite}{{\bf \color{red} []}}
\newcommand{\rvec}{\mathbf{r}}
\newcommand{\kvec}{\mathbf{k}}
\newcommand{\thetavec}{\boldsymbol \theta}
\newcommand\V{\Phi}
\newcommand\Vk{\tilde\Phi(\kvec)}
\newcommand\volume{V}
\newcommand\pfull{\ensuremath{p_{\text{full}}}}
\newcommand\pempty{\ensuremath{p_{\text{empty}}}}
\newcommand\mufull{\ensuremath{\mu_{\text{full}}}}
\newcommand\muempty{\ensuremath{\mu_{\text{empty}}}}
\newcommand\rhofull{\ensuremath{\rho_{\text{full}}}}
\newcommand\rhoempty{\ensuremath{\rho_{\text{empty}}}}
\newcommand\gst{\ensuremath{\Delta g_{st}}}

\newcommandx{\jordan}[2][1=inline]{\todo[linecolor=gray,backgroundcolor=gray!25,bordercolor=gray,#1]{\textbf{Jordan says:} #2} }
\newcommandx{\corysays}[2][1=inline]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green,#1]{\textbf{Cory says:} #2} }

\newcommandx{\maybecut}[1]{\begin{mdframed}[backgroundcolor=cyan!24]\textbf{Maybe cut:} #1\end{mdframed} }

\newtheorem{limitation}{Limitation}

@@

\title{Advancing Renewable Gas Storage using Flat-histogram Methods}
\author{Jordan K. Pommerenck}
\degree{Doctor of Philosophy}
\doctype{Dissertation}
\department{Physics}
\depttype{Department}
\depthead{Head}
\major{Physics}
\advisor{David Roundy}
\submitdate{June 8, 2020}
\commencementyear{2020}
\abstract{\input{abstract.tex}}
\acknowledgements{\input{acknowledgements.tex}}
\contributors{\input{contributors.tex}}

@@

\begingroup
\let\clearpage\relax
\begin{center}
\large
Advancing Renewable Gas Storage using Flat-histogram Methods
\normalsize
\end{center}
\chapter{Introduction}
\input{introduction.tex}
\endgroup

\chapter{Stochastic Approximation Monte Carlo with a Dynamic Update
Factor}
\vspace*{2.0cm}

\textbf{Authors:} \\
Jordan K. Pommerenck, Tanner T. Simpson, Michael A. Perlin,
and David Roundy

\vspace*{4.0cm}

\textbf{Physical Review E} \\
\href{https://doi.org/10.1103/PhysRevE.101.013301}{Journal Online Access} \\
\textbf{101(1)}, 013301 (2020)~\cite{pommerenck2020stochastic}

\clearpage{}

\input{../square-well/sq-well-body.tex}

\chapter{Flat-histogram method comparison on 2D Ising Model
}
\input{../ising/ising-body.tex}

\chapter{An upper bound to gas storage and delivery via pressure-swing
adsorption in porous materials}
\input{../gas-adsorption/gas-ads-body.tex}

\chapter{Conclusion}
\input{conclusion.tex}

\bibliographystyle{plain}
\bibliography{thesis}

\appendix
\input{../gas-adsorption/gas-ads-appendix.tex}
\end{document}
